Structured Versus Decorated Cospans

### 2021-04-18 cospans_new.tex
Minor changes

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
We apply \cref{lem:shulman} to a bifibration $\Phi \maps (\A/U) \to \A$ which we now define. Let $(\A/U)$ be the comma category in which:
\begin{enumerate}
\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$, and}
\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(a',x',a' \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to a'$ and $\alpha \colon x \to x'$ such that the following square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$a'$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1.5,-1) {$U(x')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge node[right]{$i'$} (D)
(C) edge node[below]{$U(\alpha)$} (D);
\end{tikzpicture}
\]}
\end{enumerate}
The functor $\Phi$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\alpha)=f$. We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
\[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1+x_2)) \]
where we have left the natural isomorphism $U(x_1)+U(x_2) \cong U(x_1+x_2)$  implicit
 in the above composite, for reasons of space. The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. It is easy to see that the functor $U_1$ can be made into a strict monoidal functor using this tensor product.

@@

The functor $\Phi$ is also an opfibration where given a morphism $f \maps a \to b$ with $(a,x,a \xrightarrow{i} U(x))$ over $a$, the cocartesian lifting of $f$ is given by 
\[ (f,\theta) \maps (a,x,a \to U(x)) \to (b,z,b \xrightarrow{\phi} U(z)) \]
where $\theta$ and $\phi$ arise from the following pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1.5,-1) {$U(x)+_a b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge [dashed] node[right]{$\phi$} (D)
(C) edge [dashed] node[above]{$\theta$} (D);
\end{tikzpicture}
\]
and the object $z$ arises from the cocartesian lifting of $\theta$ through $U$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (2.5,0) {$c$};
\node (C) at (1.5,1) {$b$};
\node (D) at (0,-2) {$U(x)$};
\node (E) at (2.5,-2) {$U(y)$};
\node (F) at (1.5,-1) {$U(z) = U(x)+_a b$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$\theta$} (F)
(F) edge [dashed] node [left] {$\exists ! \psi$} (E)
(D) edge node [above] {$U(g')$} (E)
(A) edge node [left] {$i$} (D)
(C) edge [dashed] node [right,near end] {$\phi$} (F)
(B) edge node {$$} (E)
(A) edge node[above]{$f'$} (B)
(C) edge node [right] {$p$} (B)
(A) edge node[left]{$f$} (C);
%(B) edge [dashed] node[right]{$$} (D)
%(C) edge [dashed] node[above]{$$} (D);
\end{tikzpicture}
\]
Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram: 
\[  (U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1+x_2)+_{a_1+a_2}(b_1+b_2). \]

Lastly, the monoidal bifibration $U_1$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$d$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
we need to show that the following square commutes up to a natural isomorphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)_a$};
\node (B) at (1.5,0) {$(\A/U)_b$};
\node (C) at (0,-1) {$(\A/U)_c$};
\node (D) at (1.5,-1) {$(\A/U)_d$};
\node (E) at (0.75,-0.5) {$\Searrow$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^*$} (C);
\end{tikzpicture}
\]
Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$. Going left, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ of $(\A/U)_a$. Then going down, we push forward along $k$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$c+_{a}U(x)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i \circ h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\psi$} (D);
\end{tikzpicture}
\]
to obtain the object $(c,z,c \xrightarrow{\psi} U(z))$ of $(\A/U)_c$, where $z \in \int F$ is given by $z=\bot_c+_{\bot_a}x$. Explicitly, $z$ is given by
\[ 1 \xrightarrow{x} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_c +_{!_a} 1)} F(c+_a U(x)) \]
and so by construction, we have that 
\[  U(z)=U(\bot_c+_{\bot_a}x)=c+_a U(x).\]
{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
 For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \colon b \to d$ by taking the following pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_{b}U(x)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\theta$} (D);
\end{tikzpicture}
\]
which yields the object $(d,z',d \xrightarrow{\theta} U(z'))$ of $(\A/U)_d$ where $z' \in \int F$ is given by $z'=\bot_d+_{\bot_b}x$. We then precompose with $f \colon c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.

Now we seek a natural isomorphism between the two objects $(c,z,c \xrightarrow{\psi} c+_a U(x))$ and $(c,z',c \xrightarrow{\theta \circ f} d+_b U(x))$ in $(\A/U)_c$. It suffices to obtain a natural isomorphism between the two objects $z=\bot_c+_{\bot_a} x$ and $z'=\bot_d+_{\bot_b} x$ in $\X$. This pushout square:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$c+_{a}U(x)$};
%\node (A') at (4,0) {$L(b)$};
%\node (B') at (6,0) {$x$};
%\node (C') at (4,-1) {$L(d)$};
%\node (D') at (6,-1) {$L(d)+_{L(b)}x$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i \circ h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\psi$} (D);
%(A') edge node[above]{$I$} (B')
%(A') edge node[left]{$L(g)$} (C')
%(B') edge node[right]{$$} (D')
%(C') edge node[below]{$\theta$} (D');
\end{tikzpicture}
\]
exhibits $c+_a U(x)$ as a pushout of the span 
\[  c \xleftarrow{k} a \xrightarrow{i \circ h} U(x) 
\]
in $\A$. We may also take the first pushout square above and paste it with the original pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_{b}U(x)$};
\node (E) at (-1.5,0) {$a$};
\node (F) at (-1.5,-1) {$c$};
\path[->,font=\scriptsize,>=angle 90]
(E) edge node [left] {$k$} (F)
(E) edge node [above] {$h$} (A)
(F) edge node [below] {$f$} (C)
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\theta$} (D);
\end{tikzpicture}
\]
obtaining a pushout square 
which exhibits $d+_b U(x)$ as a pushout of the same span in $\A$.  The resulting natural isomorphism $\kappa$ between $c+_a U(x)$ and $d+_b U(x)$ then extends to a natural isomorphism between $z=\bot_c +_{\bot_a} x$ and $z'=\bot_d +_{\bot_b} x$ in $\X$:
\[
\begin{tikzpicture}[scale=1.5]
\node () at (5,0) {$\cong$};
\node (A) at (0,0) {$1$};

@@

\path[->,font=\scriptsize,>=angle 90]
(A) edge node[fill=white]{$x$} (A1)
(A) edge node[fill=white]{$x$} (B1)

@@

\end{tikzpicture}
\]
and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $U_1$ satisfies the Beck--Chevalley condition.
\end{proof}

@@

From the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \colon (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \colon \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$. We can do the same for the other symmetric lax monoidal pseudofunctor $F' \colon \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \colon (\A'/U') \to \A'$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)$};
\node (B) at (2,0) {$(\A'/U')$};
\node (C) at (0,-1.5) {$\A$};
\node (D) at (2,-1.5) {$\A'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\Phi$} (C)
(B) edge node[right]{$\Phi'$} (D)
(C) edge node[above]{$H$} (D);
\end{tikzpicture}
\]
We construct a strong monoidal functor $G \colon (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute. Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then by a 2-functor $\mathbf{Fr} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008} will yield a map $$\mathbf{Fr}(G,H) \colon \mathbf{Fr}(\Phi) \to \mathbf{Fr}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbf{Fr}(\Phi)=F\lCsp$ and $\mathbf{Fr}(\Phi')= F'\lCsp$.

The monoidal comma category $(\A/U)$ has:
\begin{enumerate}
\item{objects as triples $(a,x,a \to U(x))$, and}
\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \colon a \to b$ and $\tau \colon x \to y$ that make the following square commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(y)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U(\tau)$} (D);
\end{tikzpicture}
\]
}
\end{enumerate}
The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1+x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. Those of $(\A'/U')$ are analogous.

@@

\item{given $(a,x,a \to U(x))$ in $(\A/U)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(x) \phi,H(a) \to U'(\theta_m E(x) \phi))$$where if $1 \xrightarrow{x} F(m)$, then $U(x)=m$ and $\theta_m E(x) \phi$ is given by 
$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(x)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
so that $U'(\theta_m E(x) \phi)=H(m)$, }

@@

\node (C) at (0,-1) {$U'(\theta_m E(x) \phi)$};
\node (D) at (3,-1) {$U'(\theta_n E(y) \phi))$};

@@

(G) edge node [below] {$y$} (I)

@@

(L) edge node[below]{$E(y)$} (D)

@@

The laxator is given by the following natural isomorphism between $\theta_m E(x) \phi + \theta_n E(y) \phi$ and $\theta_{m+n} E(x+y) \phi$:

@@

\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{x_1,x_2}} \cong}$};

@@

(B) edge node [above] {$E(x) \times E(y)$} (E)
(D) edge node [above] {$E(x \times y)$} (F)

@@

(A2) edge node [above] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)

>>>>

\begin{proof}[Proof of \cref{thm:decorated_cospans_1}] 
We apply \cref{lem:shulman} to a bifibration $\Phi \maps (\A/U) \to \A$ which we now define. The functor $U \colon \inta F \to \A$ is the associated monoidal opfibration of the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$. Let $(\A/U)$ be the comma category in which:
\begin{enumerate}
\item{an object is a triple $(a,x,a \xrightarrow{i} U(x))$ with $a \in \A$ and $x=(a',p) \in \A \times F(a')$, and}
\item{a morphism from $(a,x,a \xrightarrow{i} U(x))$ to $(b,x',b \xrightarrow{i'} U(x'))$ is a pair of morphisms $f \colon a \to b$ and $\alpha \colon x \to x'$ such that the following square commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1.5,-1) {$U(x')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge node[right]{$i'$} (D)
(C) edge node[below]{$U(\alpha)$} (D);
\end{tikzpicture}
\]}
\end{enumerate}
The functor $\Phi$ is defined on objects by $\Phi(a,x,a \xrightarrow{i} U(x))=a$ and on morphisms by $\Phi(f,\alpha)=f$. We have a monoidal structure on the comma category $(\A/U)$ where the tensor product of two objects $(a_1,x_1,a_1 \xrightarrow{i_1} U(x_1))$ and $(a_2,x_2,a_2 \xrightarrow{i_2} U(x_2))$ is given by
\[  (a_1,x_1,a_1 \xrightarrow{i_1} U(x_1)) \otimes (a_2,x_2,a_2 \xrightarrow{i_2} U(x_2)) = (a_1+a_2,x_1 \otimes x_2,a_1+a_2 \xrightarrow{i_1+i_2} U(x_1 \otimes x_2)) \]
where we have left the equality $U(x_1)+U(x_2) = U(x_1 \otimes x_2)$ implicit in the above composite, for reasons of space. The monoidal unit is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. It is easy to see that the functor $\Phi$ can be made into a strict monoidal functor using this tensor product.

@@

The functor $\Phi$ is also an opfibration where given a morphism $f \maps a \to b$ with $(a,x,a \xrightarrow{i} U(x))$ over $a$, the cocartesian lifting of $f$ is given by 
\[ (f,\theta) \maps (a,x,a \to U(x)) \to (b,z,b \xrightarrow{\phi} U(z)) \]
where $\theta$ and $\phi$ arise from the following pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1.5,-1) {$U(x)+_a b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$i$} (C)
(B) edge [dashed] node[right]{$\phi$} (D)
(C) edge [dashed] node[above]{$\theta$} (D);
\end{tikzpicture}
\]
and the object $z$ arises from the cocartesian lifting of $\theta$ through $U$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (2.5,0) {$c$};
\node (C) at (1.5,1) {$b$};
\node (D) at (0,-2) {$U(x)$};
\node (E) at (2.5,-2) {$U(y)$};
\node (F) at (1.5,-1) {$U(z) = U(x)+_a b$};
\path[->,font=\scriptsize,>=angle 90]
(D) edge node [above] {$\theta$} (F)
(F) edge [dashed] node [left] {$\exists ! \psi$} (E)
(D) edge node [above] {$U(g')$} (E)
(A) edge node [left] {$i$} (D)
(C) edge [dashed] node [right,near end] {$\phi$} (F)
(B) edge node {$$} (E)
(A) edge node[above]{$f'$} (B)
(C) edge node [right] {$p$} (B)
(A) edge node[left]{$f$} (C);
%(B) edge [dashed] node[right]{$$} (D)
%(C) edge [dashed] node[above]{$$} (D);
\end{tikzpicture}
\]
Denoting the cocartesian lifting of a morphism $f$ by $\textnormal{cocart}(f)$, we have that $\textnormal{cocart}(f_1) \otimes \textnormal{cocart}(f_2) \cong \textnormal{cocart}(f_1+f_2)$ by the universal map between two colimits of the same diagram: 
\[  (U(x_1)+_{a_1}b_1)+(U(x_2)+_{a_2}b_2) \cong U(x_1 \otimes x_2)+_{a_1+a_2}(b_1+b_2). \]

Lastly, the monoidal bifibration $\Phi$ satisfies the Beck--Chevalley condition. Given a pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$b$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$d$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$g$} (D)
(C) edge node[below]{$f$} (D);
\end{tikzpicture}
\]
we need to show that the following square commutes up to a natural isomorphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)_a$};
\node (B) at (1.5,0) {$(\A/U)_b$};
\node (C) at (0,-1) {$(\A/U)_c$};
\node (D) at (1.5,-1) {$(\A/U)_d$};
\node (E) at (0.75,-0.5) {$\Searrow$};
\path[->,font=\scriptsize,>=angle 90]
(B) edge node[above]{$h^*$} (A)
(A) edge node[left]{$k_!$} (C)
(B) edge node[right]{$g_!$} (D)
(D) edge node[below]{$f^*$} (C);
\end{tikzpicture}
\]
Let $(b,x,b \xrightarrow{i} U(x))$ be an object of $(\A/U)_b$ where $x=(b',p) \in \A \times F(b')$ so that $U(x)=b'$. Going left, we precompose with $h \colon a \to b$ to obtain the object $(a,x,a \xrightarrow{i \circ h} U(x))$ of $(\A/U)_a$. Then going down, we push forward along $k$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$c+_{a}U(x)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i \circ h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\psi$} (D);
\end{tikzpicture}
\]
to obtain the object $(c,z,c \xrightarrow{\psi} U(z))$ of $(\A/U)_c$, where $z \in \A \times F(c+_a U(x))$ is given by $z=(c+_a U(x),q)$ where $q$ is given by
\[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_c +_{!_a} 1)} F(c+_a U(x)). \]
%and so by construction, we have that 
%\[  U(z)=U(\bot_c+_{\bot_a}x)=c+_a U(x).\]
%{\john Need to refer to a proposition where we show $U$ preserves pushouts strictly.}
 For the other route, first going down, we push the object $(b,x,b \xrightarrow{i} U(x))$ forward along $g \colon b \to d$ by taking the following pushout:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_{b}U(x)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\theta$} (D);
\end{tikzpicture}
\]
which yields the object $(d,z',d \xrightarrow{\theta} U(z'))$ of $(\A/U)_d$ where $z' \in \A \times F(d+_b U(x))$ is given by ${z'=(d+_b U(x),q')}$ where $q'$ is given by 
\[ 1 \xrightarrow{p} F(U(x)) \xrightarrow{F(\zeta)} F(0+_0 U(x)) \xrightarrow{F(!_d +_{!_b} 1)} F(d+_b U(x)). \]
We then precompose with $f \colon c \to d$ to obtain the object $(c,z',c \xrightarrow{\theta \circ f} U(z'))$ of $(\A/U)_c$.

Now we seek a natural isomorphism between the two objects $(c,z,c \xrightarrow{\psi} c+_a U(x))$ and $(c,z',c \xrightarrow{\theta \circ f} d+_b U(x))$ in $(\A/U)_c$. It suffices to obtain a natural isomorphism between the two objects $z$ and $z'$ in $\X$. This pushout square:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$c$};
\node (D) at (1.5,-1) {$c+_{a}U(x)$};
%\node (A') at (4,0) {$L(b)$};
%\node (B') at (6,0) {$x$};
%\node (C') at (4,-1) {$L(d)$};
%\node (D') at (6,-1) {$L(d)+_{L(b)}x$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i \circ h$} (B)
(A) edge node[left]{$k$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\psi$} (D);
%(A') edge node[above]{$I$} (B')
%(A') edge node[left]{$L(g)$} (C')
%(B') edge node[right]{$$} (D')
%(C') edge node[below]{$\theta$} (D');
\end{tikzpicture}
\]
exhibits $c+_a U(x)$ as a pushout of the span 
\[  c \xleftarrow{k} a \xrightarrow{i \circ h} U(x) 
\]
in $\A$. We may also take the first pushout square above and paste it with the original pushout square in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$b$};
\node (B) at (1.5,0) {$U(x)$};
\node (C) at (0,-1) {$d$};
\node (D) at (1.5,-1) {$d+_{b}U(x)$};
\node (E) at (-1.5,0) {$a$};
\node (F) at (-1.5,-1) {$c$};
\path[->,font=\scriptsize,>=angle 90]
(E) edge node [left] {$k$} (F)
(E) edge node [above] {$h$} (A)
(F) edge node [below] {$f$} (C)
(A) edge node[above]{$i$} (B)
(A) edge node[left]{$g$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[below]{$\theta$} (D);
\end{tikzpicture}
\]
obtaining a pushout square 
which exhibits $d+_b U(x)$ as a pushout of the same span in $\A$.  The resulting natural isomorphism $\kappa$ between $c+_a U(x)$ and $d+_b U(x)$ then extends to a natural isomorphism between $z=(c+_a U(x),q)$ and $z'=(d+_b U(x),q')$ in $\X$:
\[
\begin{tikzpicture}[scale=1.5]
\node () at (5,0) {$\cong$};
\node (A) at (0,0) {$1$};

@@

\path[->,font=\scriptsize,>=angle 90]
(A) edge node[fill=white]{$p$} (A1)
(A) edge node[fill=white]{$p$} (B1)

@@

\end{tikzpicture}
\]
and consequently a natural isomorphism between our two objects of $(\A/U)_c$, showing that $\Phi$ satisfies the Beck--Chevalley condition.
\end{proof}

@@

From the symmetric lax monoidal pseudofunctor $F \colon \A \to \Cat$, we can obtain a Beck-Chevalley symmetric monoidal opfibration $\Phi \colon (\A/U) \to \A$ as in \cref{thm:decorated_cospans_1}, where $U \colon \int F \to \A$ is the associated monoidal opfibration of the pseudofunctor $F$. We can do the same for the other symmetric lax monoidal pseudofunctor $F' \colon \A' \to \Cat$ to obtain another Beck-Chevalley symmetric monoidal opfibration $\Phi' \colon (\A'/U') \to \A'$.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(\A/U)$};
\node (B) at (2,0) {$(\A'/U')$};
\node (C) at (0,-1.5) {$\A$};
\node (D) at (2,-1.5) {$\A'$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\Phi$} (C)
(B) edge node[right]{$\Phi'$} (D)
(C) edge node[above]{$H$} (D);
\end{tikzpicture}
\]
We construct a strong monoidal functor $G \colon (\A/U) \to (\A'/U')$ between the monoidal comma categories $(\A/U)$ and $(\A'/U')$ that will make the induced square commute. Such a commutative square is a morphism in the 2-category $\mathbf{FMF}$ of monoidal bifibrations satisfying the Beck-Chevalley condition which then, by a 2-functor $\mathbb{F}\mathbf{r} \colon \mathbf{FMF} \to \mathbf{FDbl}$ due to Shulman \cite[Theorem 14.11]{Shulman2008}, will yield a map $$\mathbb{F}\mathbf{r}(G,H) \colon \mathbb{F}\mathbf{r}(\Phi) \to \mathbb{F}\mathbf{r}(\Phi')$$between the fibrant symmetric monoidal double categories $\mathbb{F}\mathbf{r}(\Phi)=F\lCsp$ and $\mathbb{F}\mathbf{r}(\Phi')= F'\lCsp$.

The monoidal comma category $(\A/U)$ has:
\begin{enumerate}
\item{objects as triples $(a,x,a \to U(x))$, and}
\item{a morphism from $(a,x,a \to U(x))$ to $(b,y,b \to U(y))$ is a pair of morphisms $f \colon a \to b$ and $\tau \colon x \to y$ that make the following square commute:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$b$};
\node (C) at (0,-1) {$U(x)$};
\node (D) at (1,-1) {$U(y)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(A) edge node[left]{$$} (C)
(B) edge node[right]{$$} (D)
(C) edge node[above]{$U(\tau)$} (D);
\end{tikzpicture}
\]
}
\end{enumerate}
The tensor product of two objects $(a_1,x_1,a_1 \to U(x_1))$ and $(a_2,x_2,a_2 \to U(x_2))$ is given by $$(a_1,x_1,a_1 \to U(x_1)) \otimes (a_2,x_2,a_2 \to U(x_2)) = (a_1+a_2,x_1+x_2,a_1+a_2 \to U(x_1 \otimes x_2)).$$The monoidal unit of $(\A/U)$ is given by $(0_\A,0_\X,0_\A \to U(0_\X))$. Those of $(\A'/U')$ are analogous.

@@

\item{given $(a,x,a \to U(x))$ in $(\A/U)$ where $x=(m,p) \in \A \times F(m)$, $$G(a,x,a \to U(x)) = (H(a),\theta_m E(p) \phi,H(a) \to U'(\theta_m E(p) \phi))$$ where $\theta_m E(p) \phi$ is given by 
$$1 \xrightarrow{\phi} E(1) \xrightarrow{E(p)} E(F(m)) \xrightarrow{\theta_m} F'(H(m))$$
so that $U'(\theta_m E(p) \phi)=H(m)$, }

@@

\node (C) at (0,-1) {$U'(\theta_m E(p) \phi)$};
\node (D) at (3,-1) {$U'(\theta_n E(q) \phi))$};

@@

(G) edge node [above] {$p$} (H)
(G) edge node [below] {$q$} (I)

@@

(L) edge node[above]{$E(p)$} (B)
(L) edge node[below]{$E(q)$} (D)

@@

The laxator is given by the following natural isomorphism between $\theta_m E(p) \phi \times \theta_n E(q) \phi$ and $\theta_{m+n} E(p \times q) \phi$:

@@

\node () at (3,-0.5) {$\scriptscriptstyle{\stackrel{E_{p,q}} \cong}$};

@@

(B) edge node [above] {$E(p) \times E(q)$} (E)
(D) edge node [above] {$E(p \times q)$} (F)

@@

(A2) edge node [below] {$\scriptscriptstyle{E(F(!_{0_\A}))}$} (A3)
